Assessing rigor and impact of research software for hiring and promotion in psychology: A comment on Gärtner et al.~(2022)

### 2023-10-04 manuscript.Rmd
add header from overleaf provided by journal

figurelist        : no
tablelist         : no
footnotelist      : no

classoption       : "man"
output            : papaja::apa6_pdf
equal_contrib: yes
header-includes: |
  \usepackage{hyperref}
repro:
  packages:
    - papaja
    - here
    - aaronpeikert/repro@5075336
    - benmarwick/wordcountaddin@e075baa
---

@@

>>>>

figurelist        : no
tablelist         : no
footnotelist      : no
csquotes          : true
babel-lang        : american
classoption       : "jou,a4paper"
header-includes:
  - |
    % Change font for whole document
    \renewcommand{\familydefault}{\rmdefault}
    \renewcommand*\rmdefault{bch}

    \usepackage[english,all,portrait,draft]{draftcopy}
    \usepackage[blocks]{authblk}

    % Add watermark for preprints at the top of each page
    % Comment out to remove preprint watermark
    %\usepackage{draftwatermark}
    %\SetWatermarkText{PREPRINT}
    %\SetWatermarkScale{0.3}
    %\SetWatermarkAngle{0}
    %\SetWatermarkVerCenter{25pt}
    %\SetWatermarkColor[rgb]{0.85,0.85,0.95}

    % Add header with journal information
    \usepackage{fancyhdr}
    \renewcommand{\headrulewidth}{0pt} 	% remove vertical line
    \setlength{\headheight}{54pt}  % increase vertical space for header
    \fancypagestyle{firststyle}
    {
       \fancyhf{} % clear all header and footer fields

    		\fancyhead[L]{\scriptsize  
    		\textit{Meta-Psychology}, 2023, vol 7, MP.201X.xxx\\\href{https://doi.org/10.15626/MP.}{https://doi.org/10.15626/MP.}\\Article type: \\Published under the CC-BY4.0 license \\
    		\smallskip
    %%%%%%%%%%%%%%%%%%%%%%%%%%%% Badges %%%%%%%%%%%%%%%%%%%%%
    		\includegraphics[scale=0.2]{badges/opendata.png}
    		\includegraphics[scale=0.2]{badges/openmaterial.png}
    		\includegraphics[scale=0.2]{badges/preregestered.png}
    		\includegraphics[scale=0.2]{badges/preregesteredplus.png}
    		}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%		
        \fancyhead[C]{\scriptsize 
            Open data: Yes\\
            Open materials: Yes \\
            Open and reproducible analysis:\\
            Open reviews and editorial process: Yes\\
            Preregistration: 
            \vspace{0.5ex}
    \\
    		\smallskip}
        \fancyhead[R]{\scriptsize   Edited by: \\
            Reviewed by: \\
            Analysis reproduced by: \\
            All supplementary files can be accessed at OSF: \\
            \href{https://doi.org/10.17605/OSF.IO/}{https://doi.org/10.17605/OSF.IO/}
            \vspace{0.5ex}
    \\
    		\smallskip}
    }
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \usepackage[]{graphicx}
    \usepackage[]{color}
    \usepackage{tikz}  % for watermark on first page

    \usepackage{alltt}
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}

    \usepackage{amsmath}  	% for advanced math displays
    \usepackage{booktabs}		% booktables

    % With that package, tables are single spaced
    \usepackage{setspace}

    \usepackage{listings}  % for inline code blocks
    \lstset{
    	basicstyle=\footnotesize\ttfamily, % the size of the fonts that are used for the code
    	breaklines=true,  % sets automatic line breaking
    	breakatwhitespace=true % sets if automatic breaks should only happen at whitespace
    }

    \usepackage{url}	% links to headings
    \usepackage{placeins} 	% flushes Figures before the next section starts
    % use command \FloatBarrier

    %% APA-style citations
    \usepackage{csquotes}
    \usepackage[backend=biber,style=apa,hyperref=true,giveninits,uniquename=init]{biblatex}
    \DeclareLanguageMapping{american}{american-apa}

    % TODO: Users must add their .bib file here
    \addbibresource{references.bib}

    % remove unwanted fields from .bib-file
    \AtEveryBibitem{	
      \clearfield{day}
      \clearfield{month}
      \clearfield{labelday}
      \clearfield{labelmonth}
    }
    %\usepackage{multicol} %unneeded, apa6 already split cols
    \raggedbottom

    \usepackage{hyperref} % should be loaded last as it redefines many Latex commands
    \hypersetup{colorlinks, urlcolor=blue, citecolor=blue}

documentclass     : "apa7"
output            :
  papaja::apa6_pdf:
    citation_package: biblatex
equal_contrib: yes
repro:
  packages:
    - papaja
    - here
    - aaronpeikert/repro@5075336
    - benmarwick/wordcountaddin@e075baa
---

@@

\thispagestyle{firststyle}
